Paper Figures and Text

### 2024-03-12 Fish Data Analysis/Paper_Figures.qmd
Cleaning up paper code and colors

light_no_ab_color = "#d4d7dd"
light_ab_color = "#f5ba9e"
dark_no_ab_color = "#5e94d4"
dark_ab_color = "#1E4371"
sim_color = "#777777"

@@

min_dist <- 0
max_dist <- 2

@@

school_data <- na.omit(school_data)

@@

                           group_by(Flow_Ablation_Darkness) %>%
                           mutate(NND_Mean_Val = mean(NND), NND_SD_Val = sd(NND),
                                  Polar_Mean_Val = mean(School_Polar), Polar_SD_Val = sd(School_Polar),
                                  Speed_Mean_Val = mean(School_Speed), Speed_SD_Val = sd(School_Speed),
                                  Area_Mean_Val = mean(Area), Area_SD_Val = sd(Area),
                                  Groups_Mean_Val = mean(Groups), Groups_SD_Val = sd(Groups),
                                  Mean_Groups_Mean_Val = mean(Mean_Groups), Mean_Groups_SD_Val = sd(Mean_Groups),
                                  Height_Mean_Val = mean(School_Height), Height_SD_Val = sd(School_Height)) %>%
                           ungroup()
```

@@

nnd_still <- ggplot(school_data %>% filter(Flow == "Still Water"),
       aes(x = interaction(Ablation,Darkness,sep=", "), y = NND,
           color = interaction(Ablation,Darkness,sep=", "),
           fill = interaction(Ablation,Darkness,sep=", ")))+
  stat_dots(side = "both", binwidth = unit(dot_binwidth, "npc")) +
  geom_point(aes(y = NND_Mean_Val), size = 5, color = "Black") +
  geom_errorbar(aes(ymin=NND_Mean_Val-NND_SD_Val, ymax=NND_Mean_Val+NND_SD_Val), width=.2, color = "Black")+
  guides(fill = guide_legend(title = "Condition")) +
  scale_fill_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color, dark_ab_color)) +
  scale_color_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color, dark_ab_color)) +
  #ggtitle("Effect of Available Senses on Nearest Neighbor Distance (NND) in Still Water") +
  xlab("") +
  ylab("School NND (BL)") +
  theme_light()+ 
  theme(legend.position = "none") +
  ylim(0,2.5)+
  stat_compare_means(comparisons = my_comparisons, label = "p.signif", hide.ns = TRUE) +
  theme(axis.text.x = element_text(size = text_size),
        axis.text.y = element_text(size = text_size),
        axis.title.y = element_text(size = text_size))+
  scale_x_discrete(labels=function(x){sub(",\\s", "\n", x)})

@@

nnd_flow <- ggplot(school_data %>% filter(Flow == "Flowing Water (2 BL/s)"),
       aes(x = interaction(Ablation,Darkness,sep=", "), y = NND,
           color = interaction(Ablation,Darkness,sep=", "),
           fill = interaction(Ablation,Darkness,sep=", ")))+
  stat_dots(side = "both", binwidth = unit(dot_binwidth, "npc")) +
  geom_point(aes(y = NND_Mean_Val), size = 5, color = "Black") +
  geom_errorbar(aes(ymin=NND_Mean_Val-NND_SD_Val, ymax=NND_Mean_Val+NND_SD_Val), width=.2, color = "Black")+
  guides(fill = guide_legend(title = "Condition")) +
  scale_fill_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color, dark_ab_color)) +
  scale_color_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color, dark_ab_color)) +
  #ggtitle("Effect of Available Senses on Nearest Neighbor Distance (NND) in Flow (2 BL/s)") +
  xlab("") +
  ylab("School NND (BL)") +
  theme_light()+ 
  theme(legend.position = "none") +
  ylim(0,2.5)+
  stat_compare_means(comparisons = my_comparisons, label = "p.signif", hide.ns = TRUE) +
  theme(axis.text.x = element_text(size = text_size),
        axis.text.y = element_text(size = text_size),
        axis.title.y = element_text(size = text_size))+
  scale_x_discrete(labels=function(x){sub(",\\s", "\n", x)})

>>>>

light_no_ab_color = "#9C9C9C"   #"#C62E65" #A1BAA4" #"#d4d7dd" 06D6A0
light_ab_color = "#f5ba9e"
dark_no_ab_color = "#5e94d4"
dark_ab_color = "#49A078"   #"#1E4371"
sim_color = "#777777"

@@

min_dist <- 0
max_dist <- 3

@@

#school_data <- na.omit(school_data)

@@

                           group_by(Flow_Ablation_Darkness) %>%
                           mutate(NND_Mean_Val = mean(NND,na.rm = T), NND_SD_Val = sd(NND,na.rm = T),
                                  Polar_Mean_Val = mean(School_Polar,na.rm = T), Polar_SD_Val = sd(School_Polar,na.rm = T),
                                  Speed_Mean_Val = mean(School_Speed,na.rm = T), Speed_SD_Val = sd(School_Speed,na.rm = T),
                                  Area_Mean_Val = mean(Area,na.rm = T), Area_SD_Val = sd(Area,na.rm = T),
                                  Groups_Mean_Val = mean(Groups,na.rm = T), Groups_SD_Val = sd(Groups,na.rm = T),
                                  Mean_Groups_Mean_Val = mean(Mean_Groups,na.rm = T), Mean_Groups_SD_Val = sd(Mean_Groups,na.rm = T),
                                  Height_Mean_Val = mean(School_Height,na.rm = T), Height_SD_Val = sd(School_Height,na.rm = T)) %>%
                           ungroup()
```

@@

nnd_still <- ggplot(school_data %>% filter(Flow == "Still Water"),
       aes(x = interaction(Ablation,Darkness,sep=", "), y = NND,
           color = interaction(Ablation,Darkness,sep=", "),
           fill = interaction(Ablation,Darkness,sep=", ")))+
  stat_dots(side = "both", binwidth = unit(dot_binwidth, "npc")) +
  geom_point(aes(y = NND_Mean_Val), size = 5, color = "Black") +
  geom_errorbar(aes(ymin=NND_Mean_Val-NND_SD_Val, ymax=NND_Mean_Val+NND_SD_Val), width=.2, color = "Black")+
  guides(fill = guide_legend(title = "Condition")) +
  scale_fill_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color, dark_ab_color)) +
  scale_color_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color, dark_ab_color)) +
  #ggtitle("Effect of Available Senses on Nearest Neighbor Distance (NND) in Still Water") +
  xlab("") +
  ylab("School NND (BL)") +
  theme_light()+ 
  theme(legend.position = "none") +
  #ylim(0,2.5)+
  stat_compare_means(comparisons = my_comparisons, label = "p.signif", hide.ns = TRUE) +
  theme(axis.text.x = element_text(size = text_size),
        axis.text.y = element_text(size = text_size),
        axis.title.y = element_text(size = text_size))+
  scale_x_discrete(labels=function(x){sub(",\\s", "\n", x)})

@@

nnd_flow <- ggplot(school_data %>% filter(Flow == "Flowing Water (2 BL/s)"),
       aes(x = interaction(Ablation,Darkness,sep=", "), y = NND,
           color = interaction(Ablation,Darkness,sep=", "),
           fill = interaction(Ablation,Darkness,sep=", ")))+
  stat_dots(side = "both", binwidth = unit(dot_binwidth, "npc")) +
  geom_point(aes(y = NND_Mean_Val), size = 5, color = "Black") +
  geom_errorbar(aes(ymin=NND_Mean_Val-NND_SD_Val, ymax=NND_Mean_Val+NND_SD_Val), width=.2, color = "Black")+
  guides(fill = guide_legend(title = "Condition")) +
  scale_fill_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color, dark_ab_color)) +
  scale_color_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color, dark_ab_color)) +
  #ggtitle("Effect of Available Senses on Nearest Neighbor Distance (NND) in Flow (2 BL/s)") +
  xlab("") +
  ylab("School NND (BL)") +
  theme_light()+ 
  theme(legend.position = "none") +
  #ylim(0,2.5)+
  stat_compare_means(comparisons = my_comparisons, label = "p.signif", hide.ns = TRUE) +
  theme(axis.text.x = element_text(size = text_size),
        axis.text.y = element_text(size = text_size),
        axis.title.y = element_text(size = text_size))+
  scale_x_discrete(labels=function(x){sub(",\\s", "\n", x)})
